Analysis paper

### 2021-06-03 analysis/analysis.Rmd
update tables

  if ("WIS" %in% names(scores)) {
    setcolorder(scores, 
                neworder = c("Target", "Horizon", "Model", "WIS"))  
  }

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 9)

>>>>

  if ("WIS" %in% names(scores)) {
    wis <- names(scores)[grepl("WIS", names(scores))]
    setcolorder(scores, 
                neworder = c("Target", "Horizon", "Model", wis))  
  }

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
         new = c("WIS - median", 
                 "WIS - sd"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[!grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
         new = c("WIS - median", 
                 "WIS - sd"))

@@

df <- eval_forecasts(
  filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline", 
  sd = TRUE, 
  quantiles = 0.5,
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type")) 
del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                        !(grepl("interval", names(df)))]
df[, (del_cols) := NULL]

setnames(df, old = c("interval_score_0.5", "interval_score_sd"), 
         new = c("WIS - median", 
                 "WIS - sd"))

@@

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 10, width = 9)
